rotation_runs2020_sam v1

### 2020-02-26 inst/documents/rotation_runs2019.Rmd
corrected bug in recording inputs for different insecticdes

nscenarios <- 10
plotyn <- 1 #allow turning plots on and off from here, may want to turn plots off if doing large number of runs

@@

  linputs <- get_one_in(linmulti, scen_num=i)

@@

  # add scenario id column and difference onto results
  # df_in_out is one row
  df_in_out <- as.data.frame(c(linputs, gens_rot=gens_rot, gens_seq=gens_seq, 
                                        gens_u_rot=gens_u_rot, gens_u_seq=gens_u_seq,
                                        mort_rot=mort_rot, mort_seq=mort_seq, id=i))

@@

  #putting results into one row of overall results dataframe
  df_res_all[i,] <- df_in_out

>>>>

nscenarios <- 200
plotyn <- 1 #allow turning plots on and off from here, may want to turn plots off if doing large number of runs

@@

  linputs <- get_one_in(linmulti, scen_num=i)
  # creating 2nd version of inputs that retains multi-insectcide strings so that can be saved in an output file as a single row
  linputs_tosave <- get_one_in(linmulti, scen_num=i, convert_diff_insecticide_strings = FALSE)

@@

  # add scenario id column and difference onto results
  # df_in_out is one row

  #2020-02-25 beware previously when insecticides are different df_in_out ended up with multiple rows with results repeated
  #which got unintentionally semi-corrected below
  #df_in_out <- as.data.frame(c(linputs, gens_rot=gens_rot, gens_seq=gens_seq, 
  #now using linputs_tosave which contains unchanged strings, and had to add stringsAsFactors = FALSE
  df_in_out <- as.data.frame(c(linputs_tosave, gens_rot=gens_rot, gens_seq=gens_seq,                                
                                        gens_u_rot=gens_u_rot, gens_u_seq=gens_u_seq,
                                        mort_rot=mort_rot, mort_seq=mort_seq, id=i), stringsAsFactors = FALSE)

@@

  #2020-02-25 beware (see above) previoulsy when insecticides are different this saved just first row of df_in_out
  #result is that correct results are saved but with just the inputs for the first insecticide
  #this shouldn't effect the output results
  #now corrected above by keeping the values for multiple different insecticides as a string
  #putting results into one row of overall results dataframe
  df_res_all[i,] <- df_in_out

### 2020-02-26 inst/documents/rotations_notes.Rmd
corrected bug in recording inputs for different insecticdes

it must happen here :
  df_in_out <- as.data.frame(c(linputs, gens_rot=gens_rot, gens_seq=gens_seq, 
                                        gens_u_rot=gens_u_rot, gens_u_seq=gens_u_seq,
                                        mort_rot=mort_rot, mort_seq=mort_seq, id=i))

@@

@@

>>>>

it must happen here in rotation_runs2019 :
  df_in_out <- as.data.frame(c(linputs, gens_rot=gens_rot, gens_seq=gens_seq, 
                                        gens_u_rot=gens_u_rot, gens_u_seq=gens_u_seq,
                                        mort_rot=mort_rot, mort_seq=mort_seq, id=i))

@@

(to be clear I don't think the above is source of an error, it just might influence ability to analyse runs with diff insecticides later)

BUT
e.g. when there are 4 insecticides df_in_out ends up with 4 rows ... & the outputs repeated
THEN this bit (i think) just saves one row so the outputs will be OK

df_res_all[i,] <- df_in_out

It's a bit of a mess though.

  #2020-02-25 BEWARE (see above) when insecticides are different this saves just first row of df_in_out
  #result is that correct results are saved but with just the inputs for the first insecticide
  #this shouldn't effect the output results, but I should try to correct
  #putting results into one row of overall results dataframe
  df_res_all[i,] <- df_in_out

# this demonstrates problem
tst <- as.data.frame(c(linputs))

How did I solve it somewhere else ?

solution may be to use linmulti which contains the strings with multiple insecticide values in.
e.g. these are the effectivenesses for the first run
linmulti$eff[1]
[1] "0.98304248759523, 0.738747693016194"

get_one_in() converts linmulti to linputs which can be used to run a simulation, but maybe I just need to take a single row from linmulti to save into the output file.

Maybe add an argument to get_one_in to be able to keep the strings ?

tst <- as.data.frame(c(linputs_tosave))

but still remaining problem that df_res_all can't store a string so it seems to store 1 instead, e.g. for eff

@@

first try to fix the issues above, or check they don't cause problems

Try to fix so that this saves multiple insecticide inputs, e.g. as c(x,y,z)
  df_in_out <- as.data.frame(c(linputs, gens_rot=gens_rot, gens_seq=gens_seq, 
                                        gens_u_rot=gens_u_rot, gens_u_seq=gens_u_seq,
                                        mort_rot=mort_rot, mort_seq=mort_seq, id=i))
